
\documentclass[a4paper]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy


% CV Info (to be customized).
\newcommand{\CVAuthor}{Ajinkya Khamkar}
\newcommand{\CVTitle}{Resume}
\newcommand{\CVWebpage}{https://khamkarajinkya.github.io}
\thispagestyle{empty}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagemode=UseOutlines,
hidelinks,
breaklink}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.com/maps/place/Park+Doral+Apartments/@39.1684389,-86.5009352,17z/data=!3m1!4b1!4m5!3m4!1s0x886c641e02d36af5:0xb2e52a6ee480eb5f!8m2!3d39.1684389!4d-86.4987465}
{2677, East $7^{th}$ Street, Bloomington, Indiana, 47408}
\par
\href{mailto:adkhamka@iu.edu}
{adkhamka@iu.edu}
\,\SubBulletSymbol\,
+1\,(812)\,606-2086
\,\SubBulletSymbol\,
Personal website:
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
{\textbf{Indiana University}},
Bloomington, Indiana

\Gap
M.S. in Data Science
\hfill
\DatestampYMD{2016}{08}{10} --
\DatestampYMD{2018}{05}{15}
\begin{Detail}
\SubBulletItem
Cumulative GPA: 3.6 / 4.0
\SubBulletItem
Awards: Data science fellowship for 2016-2017, 2017-2018.
\end{Detail}

\BigGap
\Entry
{\textbf{University of Mumbai}},
Mumbai, India

\Gap
B.S. in Computer Science
\hfill
\DatestampYMD{2011}{08}{10} --
\DatestampYMD{2015}{05}{15}
\begin{Detail}
\SubBulletItem
Cumulative GPA: 3.6 / 4.0
\end{Detail}
\Gap


%%%%%%%%%%%%%%
%% Projects %%
%%%%%%%%%%%%%%

\Section
{Projects}
{Projects}
{PDF:Projects}
\Gap
\Entry
\href{https://khamkarajinkya.github.io/work}
{\textbf{Link to additional projects}}

Amazon back order predictions
\begin{Detail}
\SubBulletItem
Tackled class inseparability using non-linear data transformations, support vector machines \ and neural networks to achieve over 90\% accuracy and over 85\% precision.
\SubBulletItem
The neural network model was built using h2o framework in R. 
\end{Detail}
\Gap

United States presidential elections-predicting voter choice
\begin{Detail}
\SubBulletItem
Designed predictive model and interactive report to estimate probability of an individual voting for a candidate \ based on his demographic characteristics and policy stance.
\SubBulletItem
Gradient boosting ensemble learner was designed in R and the report was designed in tableau.
\end{Detail}
\Gap

Forecasting unemployment rate using Long short term memory networks
\begin{Detail}
\SubBulletItem
Designed recurrent neural network model in python to forecast unemployment rate. Model's performance was excellent with a RMSE error of less than 0.05.
\end{Detail}
\Gap

Image classification and localization using deep convolutional neural networks 
\begin{Detail}
\SubBulletItem
Designed deep learning network to classify the PASCAL VOC 2007 data set. Image localization was performed using bounding boxes and regional convolutional networks.
\SubBulletItem
Model was built using Keras library with tensorflow architecture in python.
\end{Detail}
\Gap

Artificial intelligence agents for board games
\begin{Detail}
\SubBulletItem
`Connect 4' agent based on increasing depth alpha-beta pruning search; agent searched at depth 7 and returned the best possible move in 3 seconds.
\SubBulletItem
Designed board game agent for partially observable environments using Davis-Putnam-Logemann-Loveland satisfiability algorithm.
\SubBulletItem
Designed board game agent for stochastic partially observable environments using Markov decision process. 
\end{Detail}
\Gap

Social media mining
\begin{Detail}
\SubBulletItem
Maximizing content sharing in connected networks by identifying influencers within the network.
\SubBulletItem
Individual influence was gauged using networks reaction towards their published content and its reach within the network.
\SubBulletItem
Proposed for the project to be used in market analysis, political polarization and targeted advertisements.
\end{Detail}
\Gap


%%%%%%%%%%%%%%%%%%%%%%
%% Work Experience  %%
%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work experience}
{Work experience}
{PDF:Work experience}

{\textbf{University of Mumbai}}, Mumbai, India
\Gap
Research assistant
\hfill
\DatestampYMD{2015}{09}{1} --
\DatestampYMD{2016}{07}{1}
\begin{Detail}
\Item
Designed unsupervised document classification algorithm using weighted corpus, inverse document frequency and document scores.
\end{Detail}

{\textbf{Holding Willey cricket website}}, Mumbai, India
\Gap
Data analyst
\hfill
\DatestampYMD{2015}{06}{1} --
\DatestampYMD{2015}{10}{1}
\begin{Detail}
\Item
Designed and implemented player database schema. Extracted information using scraping techniques. Performed data cleaning and uploading.
\Item
Increased user base by improving social media participation. Optimizing content delivery at time of maximum user traffic.
\end{Detail}

\Section
{Professional Communities}
{Professional Communities}
{PDF:Professional Communities}


{\textbf{Association of Information Science and Technology}}, Indiana University
\Gap
\SubBulletItem
President
\hfill
\DatestampYMD{2017}{06}{23} --
\DatestampYMD{2018}{05}{15}
\Gap
{\textbf{Computer Society of India}}, University of Mumbai
\Gap
\SubBulletItem
General Secretary
\hfill
\DatestampYMD{2012}{08}{01} --
\DatestampYMD{2014}{08}{01}


%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
{\textbf{Language:}} R, python, SAS, Stata
\Gap
{\textbf{Visualization:}} Tableau
\Gap
{\textbf{Database:}} SQL, SQLite
\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%
\end{document}
